The \kplr\ Catalog: Systematic probabilistic parameter estimation for every \kepler\ planet candidate

### 2013-11-26 document/ms.tex

\title{%
The \kplr\ Catalog:
Systematic probabilistic parameter estimation for all \kepler\ planet
candidates and inference of the radius distribution
}

@@

\begin{abstract}

We provide a catalog of probabilistic constraints on the physical parameters
of each of the planet candidates found using data from the \kepler\ transiting
planet search.
Using a physically motivated generative model with flat ``default'' priors, we
draw samples from the posterior probability distribution conditioned on all
the available light curves from \kepler\ Quarters 0 through 16.
We release both the catalog values and full posterior samplings for each
system.
We compare our results to the existing KOI catalog and find xxx.
Using these samplings, we demonstrate a computationally tractable hierarchical
inference technique for simultaneously modeling the exoplanet radius
distribution and the selection function of the \kepler\ survey and pipeline.
When applied to a sample of cool stars with well constrained properties, we
find yyy.

>>>>

\title{%
The \kplr\ Catalog:
Systematic probabilistic parameter estimation for every \kepler\ planet candidate
}

@@

\begin{abstract} % should be aims, methods, results
As precise as \kepler\ is,
it provides only probabilistic information
about transiting companions in the lightcurves of stars.
The official \kepler\ best-fit values for the parameters
(periods, radii ratios, durations, impact parameters)
contain some known biases,
are not associated with full uncertainty propagation,
and cannot be used as the basis of any probabilistic population analysis.

Here we provide a catalog of probabilistic constraints on the physical parameters
for every planet candidate (KOI) from the \kepler\ transiting
planet search.
Using a physically motivated generative model with flat ``interim'' priors, we
draw samples from the posterior probability distribution conditioned on all
the available light curves from \kepler\ Quarters 0 through 16.
We release both the catalog values and full $16384$-element posterior samplings for each
system.
We compare our results to the existing KOI Catalog and find xxx.
Using these samplings, we demonstrate a computationally tractable hierarchical
inference technique for simultaneously modeling the exoplanet radius
distribution and the selection function of the \kepler\ survey and pipeline.
When applied to a sample of cool stars with well constrained properties, we
find yyy.
